Efficient ancestry and mutation simulation with msprime 1.0

### 2021-09-10 paper.tex
Made affils easier to copy
Drop Ivan from author list for preprint
Update dev section to acknowledge gender skew
Text mainly developed by @cdquinto, @agladstein, @gtsambos and
@petrelharp

Closes #191

% Middle Authors
\author[8]{Bjarki Eldon}
\author[9]{Castedo E. Ellerman}
\author[10,11]{Jared G. Galloway}
\author[12,13]{Ariella L. Gladstein}
\author[14]{Gregor Gorjanc}
\author[15]{Bing Guo}
\author[7]{Ben Jeffery}
\author[16]{Warren W. Kretzschmar}
\author[17]{Ivan Krukov}
\author[2]{Konrad Lohse}
\author[18]{Michael Matschiner}
\author[17]{Dominic Nelson}
\author[19]{Nathaniel S. Pope}
\author[20]{Consuelo D. Quinto-Cort\'es}
\author[10]{Murillo F. Rodrigues}
\author[21]{Kumar Saunack}
\author[22]{Thibaut Sellinger}
\author[23]{Kevin Thornton}
\author[9]{Hugo van Kemenade}
\author[7,24]{Anthony W. Wohns}
\author[7]{H. Yan Wong}

% Senior Authors
\author[16,$\dagger$]{Simon Gravel}
\author[10,$\dagger$]{Andrew D. Kern}
\author[25,$\dagger$]{Jere Koskela}
\author[10,26,$\dagger$]{Peter L. Ralph}

@@

% Bjarki
\affil[8]{Leibniz Institute for Evolution and Biodiversity
Science, Museum f\"ur Naturkunde Berlin }
% Castedo, Hugo
\affil[9]{No affiliation}
% Jared, Murillo, Peter, Andy
\affil[10]{Institute of Ecology and Evolution, Department of Biology,
    University of Oregon}
% Jared
\affil[11]{Computational Biology Program, Fred Hutchinson Cancer Research
Center, Seattle, WA 98102, USA}
% Ariella
\affil[12]{Department of Genetics, University of North Carolina at Chapel Hill}
\affil[13]{Embark Veterinary, Inc., Boston}
% Gregor
\affil[14]{The Roslin Institute and Royal (Dick) School of Veterinary Studies,
    University of Edinburgh}
% Bing
\affil[15]{Institute for Genome Sciences, University of Maryland School of
Medicine, Baltimore, MD}
% Winni
\affil[16]{Center for Hematology and Regenerative Medicine, Karolinska Institute}
% Simon, Dom, Ivan
\affil[17]{Department of Human Genetics, McGill University}
% Michael
\affil[18]{Natural History Museum, University of Oslo}
% Nathaniel
\affil[19]{Department of Entomology, Pennsylvania State University}
% Consuelo
\affil[20]{National Laboratory of Genomics for Biodiversity (LANGEBIO),
    Unit of Advanced Genomics, CINVESTAV, Irapuato, Mexico}
% Saunack
\affil[21]{IIT Bombay, India}
% Thibaut
\affil[22]{Professorship for Population Genetics, Department of Life Science Systems, Technical University of Munich}
% Kevin
\affil[23]{Ecology and Evolutionary Biology, University of California Irvine}
% Wilder 2
\affil[24]{Broad Institute of MIT and Harvard}
% Jere
\affil[25]{Department of Statistics, University of Warwick}
% Peter (second affil)
\affil[26]{Department of Mathematics, University of Oregon}

@@

>>>>

% Middle Authors
\author[8]{Bjarki Eldon}
\author[9]{Castedo E. Ellerman}
\author[10,11]{Jared G. Galloway}
\author[12,13]{Ariella L. Gladstein}
\author[14]{Gregor Gorjanc}
\author[15]{Bing Guo}
\author[7]{Ben Jeffery}
\author[16]{Warren W. Kretzschmar}
% Haven't been able to contact Ivan, so forced to drop for preprint
% \author[17]{Ivan Krukov}
\author[2]{Konrad Lohse}
\author[17]{Michael Matschiner}
\author[18]{Dominic Nelson}
\author[19]{Nathaniel S. Pope}
\author[20]{Consuelo D. Quinto-Cort\'es}
\author[10]{Murillo F. Rodrigues}
\author[21]{Kumar Saunack}
\author[22]{Thibaut Sellinger}
\author[23]{Kevin Thornton}
\author[9]{Hugo van Kemenade}
\author[7,24]{Anthony W. Wohns}
\author[7]{H. Yan Wong}

% Senior Authors
\author[18,$\dagger$]{Simon Gravel}
\author[10,$\dagger$]{Andrew D. Kern}
\author[25,$\dagger$]{Jere Koskela}
\author[10,26,$\dagger$]{Peter L. Ralph}

@@

% Bjarki
\affil[8]{Leibniz Institute for Evolution and Biodiversity Science, Museum f\"ur Naturkunde Berlin }
% Castedo, Hugo
\affil[9]{No affiliation}
% Jared, Murillo, Peter, Andy
\affil[10]{Institute of Ecology and Evolution, Department of Biology, University of Oregon}
% Jared
\affil[11]{Computational Biology Program, Fred Hutchinson Cancer Research
Center, Seattle, WA 98102, USA}
% Ariella
\affil[12]{Department of Genetics, University of North Carolina at Chapel Hill}
\affil[13]{Embark Veterinary, Inc., Boston}
% Gregor
\affil[14]{The Roslin Institute and Royal (Dick) School of Veterinary Studies, University of Edinburgh}
% Bing
\affil[15]{Institute for Genome Sciences, University of Maryland School of Medicine, Baltimore, MD}
% Winni
\affil[16]{Center for Hematology and Regenerative Medicine, Karolinska Institute}
% Michael
\affil[17]{Natural History Museum, University of Oslo}
% Simon, Dom, Ivan
\affil[18]{Department of Human Genetics, McGill University}
% Nathaniel
\affil[19]{Department of Entomology, Pennsylvania State University}
% Consuelo
\affil[20]{National Laboratory of Genomics for Biodiversity (LANGEBIO), Unit of Advanced Genomics, CINVESTAV, Irapuato, Mexico}
% Saunack
\affil[21]{IIT Bombay, India}
% Thibaut
\affil[22]{Professorship for Population Genetics, Department of Life Science Systems, Technical University of Munich}
% Kevin
\affil[23]{Ecology and Evolutionary Biology, University of California Irvine}
% Wilder 2
\affil[24]{Broad Institute of MIT and Harvard}
% Jere
\affil[25]{Department of Statistics, University of Warwick}
% Peter (second affil)
\affil[26]{Department of Mathematics, University of Oregon}

@@

A important goal of the msprime development model is to maximise
accessibility for prospective users and contributors. However, it is important
to acknowledge that under-representation persists in population genetics,
especially in methodology and open-source software
development~\citep{trinkenreich2021women}. The authorship
of our paper reflects this with a skew towards men and affiliations in the USA
and Europe. We know the importance of creating and strengthening networks to
develop and maintain a diverse community of contributors, and we are committed
to fostering a supportive collaborative environment that helps to address these
inequalities in our field.
